\documentclass[addpoints,12pt]{exam}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{amsmath,esint}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage{charter}
\usepackage{mathpazo}
% \usepackage[inline]{enumitem}
%\usepackage[bitstream-charter]{mathdesign}	% fonts in use

\pagestyle{headandfoot}
\runningheadrule
%\firstpageheader{\footnotesize CS 314}{\footnotesize Page \thepage\ of 
%\numpages}{\footnotesize January 28, 2015}
%\firstpageheadrule
\runningheader{\footnotesize Year 7 Mathematics}{\footnotesize Test 1, Page \thepage\ of 
\numpages}{\footnotesize September 11, 2017}
%\firstpagefooter{}{}{}
%\runningfooter{}{}{}

%\pointsinmargin		% print answers in the margin
\printanswers		% print answers to questions

\bracketedpoints
\pointsinrightmargin
% \qformat{Question \totalpoints\ points}
    
\begin{document}
\begin{center}\centering
    {\large DAYSPRING INTERNATIONAL ACADEMY}\\
    Mathletics for Lower Secondary\\
%     \textbf{Class Test}
\end{center}

\begin{center}
  \fbox{\fbox{\parbox{6in}{
  Read this question \emph{carefully}. You have 7 minutes to answer write your solution on this 
paper as well solution on the board provided.}}}
\end{center}
\vspace{0.3in}
\makebox[\textwidth]{\textbf{Group's Name}:\enspace\hrulefill}
\vspace*{0.2in}
\makebox[\textwidth]{Quiz Master's Name: Mr. Charles Fiende\enspace\hfill}\\
\textbf{Time Allowed: 7 minutes}

\begin{questions}
  
 \question \emph{Challenge Problem.} Anna was planning how to seat guests at a dinner. There 
were between $50$ and $100$ people coming. Anna noticed that they could be seated with $8$ people 
to a table and no seats left empty. She also noticed that they could be seated with $12$ people to 
a table with no seats left empty. What is the highest possible number of guests coming?
	\ifprintanswers
	  \begin{solution}\\
		This is a problem of LCM. Hence the prime factors of the numbers are
		\begin{align*}
		  8 &= 2\times2\times2 \\
		  12 &= 2\times2\times3 \\
		  \text{LCM} &= 2\times2\times2\times3 = 24
		\end{align*}
	Now if the number of guests coming is between $50$ and $100$, then their number will be a 
multiple of $24$. $24\times4=96$ which is between $50$ and $100$.
	  \end{solution}
	\else
	  \makeemptybox{5.3in}
	\fi
	
  
\end{questions}
% \vspace*{1cm}
%\centering\gradetable[h][questions]

\end{document}